### Medical categories

```{r}
#| label: data-mesh-terms
df_mesh <- read_csv(here("data", glue("{params$project_name}_publications_mesh.csv")),
                    show_col_types = FALSE)

mesh_summary_results <- mesh_summary(df_mesh)
outputs_with_at_least_one_mesh_term <- mesh_summary_results$outputs_with_at_least_one_mesh_term
n_unique_mesh_terms <- mesh_summary_results$n_unique_mesh_terms
outputs_with_no_mesh_term <- mesh_summary_results$outputs_with_no_mesh_term
top_k_mesh_terms <- mesh_summary_results$top_k_mesh_terms
```

```{r}
#| label: data-rcdc
df_rcdc <- read_csv(here("data", glue("{params$project_name}_publications_rcdc.csv")),
                    show_col_types = FALSE)

rcdc_summary_results <- rcdc_summary(df_rcdc, p = 1)
outputs_with_at_least_one_rcdc <- rcdc_summary_results$outputs_with_at_least_one_rcdc
outputs_with_no_rcdc <- rcdc_summary_results$outputs_with_no_rcdc
n_unique_rcdc <- rcdc_summary_results$n_unique_rcdc
top_k_rcdc <- rcdc_summary_results$top_k_rcdc
```

```{r}
#| label: data-hrcs-hc
df_hrcs_hc <- read_csv(here("data", glue("{params$project_name}_publications_hrcs_hc.csv")),
                       show_col_types = FALSE)

hrcs_hc_summary_results <- hrcs_hc_summary(df_hrcs_hc, p = 1)
outputs_with_at_least_one_hrcs_hc <- hrcs_hc_summary_results$outputs_with_at_least_one_hrcs_hc
outputs_with_no_hrcs_hc <- hrcs_hc_summary_results$outputs_with_no_hrcs_hc
n_unique_hrcs_hc <- hrcs_hc_summary_results$n_unique_hrcs_hc
top_k_hrcs_hc <- hrcs_hc_summary_results$top_k_hrcs_hc
```

```{r}
#| label: data-hrcs-rac
df_hrcs_rac <- read_csv(here("data", glue("{params$project_name}_publications_hrcs_rac.csv")),
                       show_col_types = FALSE)

hrcs_rac_summary_results <- hrcs_rac_summary(df_hrcs_rac, p = 1)
outputs_with_at_least_one_hrcs_rac <- hrcs_rac_summary_results$outputs_with_at_least_one_hrcs_rac
outputs_with_no_hrcs_rac <- hrcs_rac_summary_results$outputs_with_no_hrcs_rac
n_unique_hrcs_rac <- hrcs_rac_summary_results$n_unique_hrcs_rac
top_k_hrcs_rac <- hrcs_rac_summary_results$top_k_hrcs_rac
```

```{r}
#| label: data-icpr-cso
df_icrp_cso <- read_csv(here("data", glue("{params$project_name}_publications_icrp_cso.csv")),
                       show_col_types = FALSE)

icrp_cso_summary_results <- icrp_cso_summary(df_icrp_cso, p = 1)
outputs_with_at_least_one_icrp_cso <- icrp_cso_summary_results$outputs_with_at_least_one_icrp_cso
outputs_with_no_icrp_cso <- icrp_cso_summary_results$outputs_with_no_icrp_cso
n_unique_icrp_cso <- icrp_cso_summary_results$n_unique_icrp_cso
top_k_icrp_cso <- icrp_cso_summary_results$top_k_icrp_cso
```

:::{.panel-tabset}

## MeSH

[Medical Subject Headings](https://www.ncbi.nlm.nih.gov/mesh/) (MeSH) is the NLM controlled vocabulary thesaurus used for indexing articles for PubMed.

A total of **`r outputs_with_at_least_one_mesh_term` outputs** in the result set are allocated at least one MeSH category, with **`r n_unique_mesh_terms` unique terms** used across these outputs. There are `r outputs_with_no_mesh_term` outputs that have not been allocated at least one MeSH term. @tbl-mesh plots the MeSH terms that account for at least 1% of the unique terms.

```{r}
#| label:  tbl-mesh
#| tbl-cap: !expr glue("The top {mesh_summary_results$k} occuring MeSH terms for research produced by the {params$research_unit}, {params$min_year} to {params$max_year}.")
#| cap-location: top
knitr::kable(top_k_mesh_terms, align = "lcc", 
             booktabs = TRUE, linesep = "\\addlinespace") %>%
  kableExtra::row_spec(0, background = "white", color = "#303030")
```

## RCDC

The [Research, Condition, and Disease Categorization](https://report.nih.gov/funding/categorical-spending/rcdc-process) (RCDC) system is used by the National Institutes of Health and is a biomedical classification system consisting of 237 categories. Of the research outputs in the result set, **`r outputs_with_at_least_one_rcdc`** are allocated at least one RCDC category, with **`r n_unique_rcdc` unique categories** used across all research outputs. @tbl-rcdc presents those RCDC categories which account for at least `r rcdc_summary_results$p`% of the total categories.

```{r}
#| label:  tbl-rcdc
#| tbl-cap: !expr glue("Research, Condition, and Disease Categories accounting for at least {rcdc_summary_results$p} per cent of the total categories assigned to research outputs produced by the {params$research_unit}, {params$min_year} to {params$max_year}.")
#| cap-location: top
#| column: page-inset-right
knitr::kable(top_k_rcdc, align = "lcc", 
             booktabs = TRUE, linesep = "\\addlinespace") %>%
  kableExtra::column_spec(1, width = "40em") %>%
  kableExtra::row_spec(0, background = "white", color = "#303030")
```

## HRCS 

The [Health Research Classification System](https://hrcsonline.net) (HRCS) is a system for classifying and analysing all types of biomedical and health related research. The HRCS was developed by the UKCRC Partners as a research management tool. The HRCS is subdivided into Health Categories (HC) and Research Activity Classifications (RAC).

Of the research outputs in the result set, **`r outputs_with_at_least_one_hrcs_hc`** are allocated to at least one health category in the HRCS, with **`r n_unique_hrcs_hc` unique categories** used across all research outputs. @tbl-hrcs-hc presents those HRCS health categories which account for at least `r hrcs_hs_summary_results$p`% of the total categories.

```{r}
#| label:  tbl-hrcs-hc
#| tbl-cap: !expr glue("HRCS Health Categories accounting for at least {hrcs_hc_summary_results$p} per cent of the total categories assigned to research outputs produced by the {params$research_unit}, {params$min_year} to {params$max_year}.")
#| cap-location: top
#| column: page-inset-right
knitr::kable(top_k_hrcs_hc, align = "lcc", 
             booktabs = TRUE, linesep = "\\addlinespace") %>%
  kableExtra::column_spec(1, width = "40em") %>%
  kableExtra::row_spec(0, background = "white", color = "#303030")
```

Of the research outputs in the result set, **`r outputs_with_at_least_one_hrcs_rac`** are allocated to at least one research activity classifications in the HCRS, with **`r n_unique_hrcs_rac` unique categories** used across all research outputs. @tbl-hrcs-rac presents those HCRS research activity classifications which account for at least `r hrcs_rac_summary_results$p`% of the total categories.

```{r}
#| label:  tbl-hrcs-rac
#| tbl-cap: !expr glue("HRCS Research Activity Classifications accounting for at least {hrcs_rac_summary_results$p} per cent of the total categories assigned to research outputs produced by the {params$research_unit}, {params$min_year} to {params$max_year}.")
#| cap-location: top
#| column: page-inset-right
knitr::kable(top_k_hrcs_rac, align = "lcc", 
             booktabs = TRUE, linesep = "\\addlinespace") %>%
  kableExtra::column_spec(1, width = "40em") %>%
  kableExtra::row_spec(0, background = "white", color = "#303030")
```

## ICRP CSO

The [Common Scientific Outline](https://www.icrpartnership.org/cso) (CSO) is a common language used by International Cancer Research Partnership (ICRP) database to code research awards, and is used to compare and contrast the research portfolios of public, non-profit, and governmental research agencies. 

Of the research outputs in the result set, **`r outputs_with_at_least_one_icrp_cso`** are allocated to at least one category in the Common Scientific Outline, with **`r n_unique_icrp_cso` unique categories** used across all research outputs. @tbl-icrp-cso presents those ICPR Common Scientific Outline categories which account for at least `r icrp_cso_summary_results$p`% of the total categories.

```{r}
#| label:  tbl-icrp-cso
#| tbl-cap: !expr glue("ICRP Common Scientific Outline categories accounting for at least {icrp_cso_summary_results$p} per cent of the total categories assigned to research outputs produced by the {params$research_unit}, {params$min_year} to {params$max_year}.")
#| cap-location: top
#| column: page-inset-right
knitr::kable(top_k_icrp_cso, align = "lcc", 
             booktabs = TRUE, linesep = "\\addlinespace") %>%
  kableExtra::column_spec(1, width = "40em") %>%
  kableExtra::row_spec(0, background = "white", color = "#303030")
```

:::